Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
tweak conclusions and future work

We demonstrated that our algorithm selection approach achieves substantial
performance improvements over the single algorithm that has the best performance
on our benchmark set. We showed that combining an algorithm selection approach
with a new incomplete variant of \LAD that is able to detect inconsistencies
and a presolver boosts performance even further. Finally, we discussed how
insights from machine learning could feed back into algorithm development.

We have yet to investigate parallel portfolios: as well as the possibility of
running multiple single-threaded solvers simultaneously, the \Glasgow
algorithms have a multi-core parallel implementation available, which can use a
configurable number of threads. Nor have we investigated variants of the
subgraph isomorphism problem---it would be interesting to see, for example,
whether similar features are important when dealing with induced or directed
isomorphisms.

>>>>

We demonstrated that our algorithm selection approach achieves substantial
performance improvements over the single algorithm that has the best performance
on our benchmark set. We showed that combining an algorithm selection approach
with a new incomplete variant of \LAD that is able to detect inconsistencies
and a presolver boosts performance even further. Finally, we showed how
insights from machine learning can guide algorithm development.

Directions for future work include scheduling multiple solvers to run instead of
a single one; in particular the \Glasgow algorithms provide a multi-core
parallel implementation, which can use a configurable number of threads. It
would also be interesting to investigate other variants of the subgraph
isomorphism problem.
